---
title: "Xaringan test"
subtitle: "with Xaringan.club resources"  
author: "shitao"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)
```

```{r xaringanExtra, echo=FALSE}
xaringanExtra::use_xaringan_extra(c("tile_view", "editable",  "animate_css", "scribble", "tachyons", "panelset", "fit_screen", "clipboard"))
```

.can-edit[You can edit this silde]

Hello, .can-edit[world], and welcome to my talk!

## A few of my favorite things

.can-edit.key-likes[
- eating
- writing
- ......
]

---
class: animated slideInRight backOutup

## This slide...

- slides in from the right 
- and fades out to the left on exit

---
layout: true

# Panelset
---

This is a panelset.

.panelset[
.panel[.panel-name[R Code]

```{r eval=FALSE}
summary(mtcats)
```

]

.panel[.panel-name[Output]

```{r echo=FALSE}
summary(mtcars)
```

]
]
---
layout: false

# test-tachyons

.bg-washed-green.b--dark-green.ba.bw2.br3.shadow-5.ph4.mt5[
The only way to write good code is to write tons of bad code first. 
Feeling shame about bad code stops you from getting to good code

.tr[
— Hadley Wickham
]]
